Current and future constraints on primordial magnetic fields

### 2017-01-25 pmf.tex
more fig updates
plot updates

\begin{figure}[htb]\centering
\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates.pdf}
  \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
  How the expected PMF changes with the spectral index, $n_B$. 
  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
  }
\end{figure}

@@

\begin{figure}[htb]\centering
\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_area.pdf}
  \caption[Insert plot of error on $A_{PMF}$ vs number of detectors]{ \label{fig:ndetector}
  How the expected PMF changes with the spectral index, $n_B$. 
  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
  }
\end{figure}

>>>>

\begin{figure}[htb]\centering
\includegraphics[width=0.4\textwidth,clip,trim={1.5cm 12.cm 5cm 4cm}]{pmf_templates_nb.pdf}
  \caption[CMB polarization from PMFs with different spectral indices]{ \label{fig:pmf-nb}
  How the expected PMF changes with the spectral index, $n_B$. 
  The lensing B-mode power spectrum (solid, black line) are plotted against the PMF power for $n_B=-2.9$ (solid, purple line), $n_B=-1$ (dashed, green line), and $n_B=+2$ (dotted, red line). 
  To keep all the curves on the same scale, we adjust the RMS strength of the magnetic field, \bpmf{}, between the three cases as noted in the legend. 
  At fixed RMS magnetic field strength, increasing $n_B$ greatly increases the expected B-mode power. 
  There is an inflection point between the nearly-scale-invariant PMF with $n_b=-2.9$ and the bluer PMF spectra ($n_b=-1$ or 2) which shifts power to smaller angular scales. 
  }
\end{figure}

@@

\begin{figure}[htb]\centering
\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_sens.pdf}
  \caption[Insert plot of error on $A_{PMF}$ vs number of detectors]{ \label{fig:ndetector}
  How the expected PMF changes with the spectral index, $n_B$. 
  The PMF B-modes are plotted against the lensing B-modes for $n_B = [-2.9, -1, 2]$. 
  The PMF power shifts to smaller angular scales as $n_B$ increases. \tbd{placeholder}
  }
\end{figure}
